### 2022-11-06 rmd/nhanes_data.Rmd
explain data size

>>>>

```{r, echo = FALSE}

n_htn <- table.glue::table_value(sum(nhanes_data$svy_subpop_htn))
n_chol <- table.glue::table_value(sum(nhanes_data$svy_subpop_chol))

Currently, two sub-populations are included in `nhanes_data`:

- blood pressure and hypertension (n = `r n_htn`)

- lipids and cholesterol (n = `r n_chol`)

To access a sub-population, simply filter `nhanes_data` to contain rows where the corresponding sub-population indicator is equal to 1, e.g.,

```{r, results='hide'}

# for blood pressure and hypertension sub-population
nhanes_data[svy_subpop_htn == 1]

# for lipids and cholesterol sub-population
nhanes_data[svy_subpop_chol == 1]
